Transforming Trash as an Artistic Act

### 2015-11-11 chapter1.tex
re-organization of arguments, artworks.
Former-commit-id: ac016aaa788eefe04be3d4d6757e10971a0c9524

%****************************************
% Structure of this chapter
% Section: explain the topic and its significance, raise curiosity, give same facts about it.
% Section: state the the purpose of this study, specify the focus of it.
% Section: overview of chapters and structure of thesis.
% Section: a note on terminology, clarification about the comprehensive terminology.

\epigraph{If I seem to be over-interested in junk, it is because I am, and I have a lot of it, too --- half a garage full of bits and broken pieces. I use these things for repairing other things\ldots But it can be seen that I do have a genuine and almost miserly interest in worthless objects. My excuse is that in this era of planned obsolescence, when a thing breaks I can usually find something in my collection to repair it --- a toilet, or a motor, or a lawn mower. But I guess the truth is that I simply like junk.}{\hfill---John Steinbeck, \textit{Travels with Charley, 1962}}

% Bence introductionda çöpün farklı şekillerde ele alınabileceğini bir şekilde göstermek gerekli. Burdaki genel geçer yaklaşımdan bahsetmek gerekli.

% Ele aldığımız çöp insanların çöpleri, günlük kullanımdaki çöpler. Çok da değerli olmayan yerine yenisi koyabileceğimiz çöpler.

@@

Western societies from periods where manual labor and long struggle required in production process and materials are reused and transformed again and again, have reached to periods where production process speeds up and becomes more accessible. Consumption habits have changed radically and have created piles of trash that is not obvious how to reuse them. In this work the practice and process of reusing and transforming trash which is an alternative to today's existing production and consumption habits is investigated. Stages and expression of this practice is examined with my artwork in the context of art.

In previous ages (pre industrial ages? which age?) objects and resources are used again and again. Production of objects are hard and laborious. \comment{Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur. Mendillere bunlara örnek olabilir. Aslında tam benim konumla ilgili çünkü tek kullanımlık. Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.} \todo{Susan Strasser}

% Trash is everywhere and, produced every time
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession (It is experienced by everybody.). During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People cares the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. They are durable(in terms of resistant to natural affects) products. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash. Live with trash. Do not see it as trash actually. Then the question is how to love trash? how to live with trash? can living with our trash enrich (our perceptions, abilities)? how not to see them as trash and useless? Can it be possible with art?)

@@

% Konunun dikkat çekici ilginç kısımları. Interesting points of the topic. Facts about the trash. Changes through the time.
% Konu hakkındaki temel bilgiler.
% Konunun ele alınan kısmı.

% Çöp ve dönüşümden bahsetmek gerekli. Çöp nedir? Dönüşüm nedir? Çöpün bir dönüşümü var mıdır? Var ise bu nasıl bir şeydir? 
% Introduce as an discussion. Trash is valueless? really? is it just a sculpture? Tons of different approaches to the trash. 
People tend to think that trash is values because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless? They do not think what happens after they throw it away. It exits from your life but not the world. What happens when you throw away a It is stacked from another place. Value of objects are not static. Trash is not static also It has a long journey. A project conducted by MIT researches journey of trash by placing trackers onto the trash. The results are surprising. Trashes spread away across the country and this journey takes month. \todo{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo{footnote what are these countries?}. In other worlds Americans trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo{consider Papua genen people}

@@

% Bu trash in every sıralamasını neden yapıyorum? Genel bir çerçeve çizmekten çok aslında evrensel bir konu olduğuna değinmiş oluyorum. Peki bu çok açık bir şey mi? Yani aslında çok da açık olmayan bilgilerek vererek yaparsam olmayabilir. Evrensel olmasının benim için ne önemi var. Yaşamımızın bir parçası demek. Tamam da buna karşı bir şey mi var. Ben göremiyorum açıkcası. Herkes bunu biliyor. Farkında mıyız. Ama farkında olmak istemediğimiz bir şey ki sürekli kendimizden uzaklaştırıyoruz. O zaman bu gerçekleri aslında ne kadar biliyoruz. Ama bunları bilmek böyle davranmamız gerektiği anlamına mı gelmektedir? Aslında yabancı olmadığımız ama uzak durduğumuz bir konu. Belki de sırf bu yüzden kaçırdığımız bir sürü şey olabilir.

Trash is global, and shared concept for all societies throughout the ages. 
\textbf{Trash in every age.} In other words it is part of human activity of every historic age. It exists early ages of human to now. Trash is part of the early days of human production / or activity. Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human. Legs, bones etc. [TODO etymology reference, see appendix] Archaeologist find things from people throw away. 
\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
% TODO look introduction of revista, there is a related reference above it.
\textbf{Trash is everywhere.}

% ARTWORK
% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuous

Why people are interested in rubbish. Some of the artist also interested in others trash. \comment{O çöplerde ne bulmayı umuyorlar ki? Aslında çöp bizim davranışlarımız, yaşayız tarzımız hakkında bize yön veriyor. ve bu her zaman fiziksel dönüştürme ile değil de aynı zamanda anlamsal ve mekansal değiştirme sorulamalarla mümkün oluyor. Bazen de olduğu gibi kullanıyorlar. bu açıdan önemli. Çöpü çöp şekliden sunan sanatçılar. Ama bu nasıl mümkün ki? fotoğrafını çekenler aslında gerçekten ona müdahele etmemiş mi oluyorlar. Bence değil? bir şekilde müdahele var gene orada. o fotoğraflarda artık dikkatin objesi haline geliyor. çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.

@@

% Wall-E belki olabilir. Dünyanın aslında bir çöp yığını haline gelmesini gösteriyor olabilir. Çöp dağları, çöp denizleri. Atılmış binbir türlü nesne. ve wall-e ise bunları ne yapıyor sadece pressleyip bir kenera bırakıyor. Bundan basetmişken aslında pressleme işi yapan şu cesar. Bu şekilde olmak zorunda mı? Bunun alternatifi yok mu? Aslında bu tezde bunlara cevap bulunabilir. Çöpe olan bir sürü yaklaşıma ek olarak bir de bunlar var. Ya da başka neler var? Bunları araştıran inceleyen bir yazı. Wall-E'nin çizdiği portreyi tekrar ele alırsak ne görürürüz. İnsanlık buna mı dönüşücek? Başka bir ihtimal yok mu? Gerçekten de dünyayı bekleyen şey bu mu? Bir çöp yığını olması mı? Bu bir abartı mı yoksa gerçeklik payı yadsınacak cinsten mi?

WALL-E is a 2008 American computer-animated science fiction comedy film produced by Pixar Animation Studios. A robot named WALL-E, who is designed to clean up an abandoned, waste-covered Earth far in the future. WALL-E resembles giant dozers that moves and piles trash in the landfills. This robot creates squeezed trash blocks that have no meaning and interpretation. All different objects in terms of their physical and social properties turned to same squeezed garbage blocks. There are mountains of trash and place is very limited. By squeezing them, WALL-E saves space. \todo{What is the context of it? Which part is related with my topic?} What are we going to do with all these mountains of trash? \todo{Can it be placed under zizek part?} WALL-E represents a possible future condition of Earth.

% TODO Life time of objects.
% Nesnelerin yaşam süreleri, Bu yaşam sürelerinin ne kadar olduğu. Burada ilginç bilgiler olabilir. Aslında ne kadar çok üretip ne kadar kısa sürede tükettiğimi görüyoruz. Ama eskiden ürünler daha uzun sürelerde kullanılıyordı. Sonrasında ise bu kısa sürede tüketilen ürünlerden nasıl dağlar oluşuyor. Çöpçü kaç günde bir ziyaret ediyor. Çöp kutuları ne kadar sürede bir doluyor. Çöp kovalarının içlerinde neler var.

\todo{Background information about the thesis. Inspirational points. The fact of trash.}

@@

% Aga çöpe farklı yaklaşımlar var. O yüzden background information olarak burada verilebilir ve scope belirlenebilir. Tam da bu noktada ise purpose kısmına geçilebilir. Çöpe nasıl yaklaşıyorlar falan filan. İşte ben tam da bu noktada sanatta nasıl yaklaşılmıştır dicem. Hatta basitçe sanatta bu tür işlere

\comment{Trash draws attention different peoples and disciplines. In other words there are different studies related with trash. Different approaches to the trash and son on. However in this thesis study trash }

There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.

% Aslında sadece bir heykel işi olan şeylerden bahsedebilirim, ya da aslında belki de içine girip dokunabildiğin bir şey olabilir.

% Savunma.
% Yani aslında bu chapterdaki fikirler vs.'ler birer supportive yaklaşımlar. neler yapılmış onları listesi. literatür taraması. ama tabi benim işime yarayanlar.

This trash pheomanan catches the attention of artist. It is very human activity. In this context which trash? What type of discard. Many type of it?

% Idea of everthing can be trash. Act of trashing. not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

%%%
%%%
%%%
\section{Purpose of the Study}

%****************************************
% It is a justification of the work. 
% What is trash? Who does call it trash? 
% Is it possible to transform it? How? Which methods?
%........................................

\todo{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}

% Bu söylemeden önce insana böyle bir şeyin mümkün olduğunu anlatmak gerekli. Yani aslında transformation of trash diye bir şey var aga demeli. Kimler bunu nasıl yapmış. Neler var ortalıkta bunlara bakmak gerekli. Pres makineleri falan. Ama bunu aynı zamanda sanatsal açıdan inceleyenler, sanatsal amaçlarla yapanlar bulunmakta demek gerekli.
The aim of this study is to explore the theories and methods in transformation of trash in the context of art and artistic act.

@@

% Çöpün sanat işlerinde kullanılmasının önemi ne? Bunun karşısındaki şey nedir? Diğer alanlardaki yaklaşımlar bir şey üretemiyor mu? Bu tezin önemi ne? Birilerinin bıraktığı boşluğu doldurmak mı? Ya da benim yaptığım işin önemi ne?

% Önceki işlere değinmek gerekli. Bu alanla ilgili yapılmış. Mesela ne var. İki tane tez buldum aslında tam da bu konuyla ilgili. Önceki işler olacak, yetersiz eksik yanları olacak ve ben onlara belli başlı eklemeler yapacağım.

As many people are inside the business of transforming trash through craft and so on. People on the streets looking for aliminu cans, glass bottles, plastic. They collect and sell them to survive. There are companies that are collect waste materials to regain them again the industry. In thesis they are not in the scope. People that give attention to the trash and behave artistic act is in the scope of this thesis.

% How does it become trash?
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%%
%%%
%%% 
\section{Overview of Chapters}
This study is structured many examples of artworks in different part of the thesis. As the related topic or argument is presented example artwork is given at this moment. Immediately how artist replies this issue is illustrated. Thereby artworks are examined in the theoretical and cultural context. Art works are used as a supportive elements for the stated arguments. \comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.}

@@

%****************************************
% About the thesis statement and focus:
% Is it too broad?
% Is it debatable? Is is fact? (Trash is not a end point of objects, there is a life waiting for them?)
% What is my side? throwing away is required for society to go further? or omitting the tons of possibilities... 
% Supporting claims?
% What is my thesis statement? Again same topic... It needs to be solved...
%........................................

%****************************************
% Some comments
% Burada önemli olan şey soru veya sorgulanan şey. Bu soru projeye yön verecek. Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek. Tartışmalar ne üzerine olmalı bu durumda? 
% The project aims to what? and what needs to justify what it questions? 
% At this point, the question of what will be in the future of photography has to be asked. Bu çok önemli, bir şeyler hazırlayıp neyin sorgulanması gerektiğini sormak gerekli.

% Tipografi ve ideoloji arasında bir ilişki vardır. Fotoğrafın geleceği? Kelime ve imaj arasındaki ilişki, beden ve algı üzerinden incelenebilir? kelime ve imaj arasında bir problem olduğundan bahsediyor. Sanat işlerinde çöp kullanmak toplum tarafından atılan şeyi tekrar kullanılabileceğini gösterebilir. Toplum ve çöp nispeten bir problemli bir durum. Burada bir dert var. Atılan tüketilen manalar var. Sanat bunları provoke mi ediyor. Peki ya ben ne öneriyorum, yani aslında bir şey önermem mi gerekiyor? Sanat ve çöp arasında nasıl bir ilişki vardır? Çöp ile diğer nesneler arasında nasıl bir ilişki vardır?

% Zaten hali hazırda sanatçılar bunu yapıyorlar, tez aslında bunları inceliyor olabilir ama tez aslında benim işimi inceliyor. İş neyi soruyor ise aslında tez de onu soruyor. Yapılan işlerle sorulan sorular arasında bir bağlantı var. Bu noktada aslında benim işin neyi sorguladığını bulmam gerekli. Çöp dönüştürülebilir, sanatsal bağlamda. (Çok geniş değil mi abi sanatsal bağlamda demek? Çöp de çok geniş bir konu.) Konuyu bir şeklide daraltmak gerekli. Çöp sanat işlerine girmiştir. Çöp dönüştürmek aslında bir artistic acte dönüşüyor. Tezde bunu anlatıyor. Aga bu artisctic act dediğin şey de ne oluyor. Çöp dönüştürmek ne oluyor?

% Çöpe yeni bir alternatif yaşam üretmek gerekli! Neden böyle düşünüyorsun? Çünkü sürekli çöp üretiyorsun ama bir yandan da bundan dert yanıyorsun. Zizek işte bu konuya el basıyor.

% Aslında hepimiz bir şeyleri dönüştürüyoruz! Neden böyle düşüyorsun? Örnekleri nelerdir? Bricologe bu iddayı destekler mi? Nesnleri üretim amaçlarından farklı amaçlar için kullanmak yeni bir şey değil. (Ama zaten ben sanat amacıyla kullanılmasından bahsedeceğim.) Belki bunu belirtmek için mantıklı olabilir. Ama burada bir farklılık var olamalı. Diğerinden ayıran diyeceğim ama öyle bir fark aramamak gerekli bence. Sanat o farkı yıkmak için uğraşıp duruyor. Belki de bu uğraşa katkısı bu olabilir bu işin. Bir şeyleri dönüştürme potansiyellerimiz olduğunu düşünebiliriz. Dönüştürme dediğimiz şey aslında hangi noktada açığa çıkıyor. Bir ihtiyaç anında, kaçış anında, ya da yeni alternatifler ararken mi?

% Çöpün dönüştürülmesi ne olaki? Buna bir şekilde girişte yer vermek gerekli. Çöpün market içindeki hareketi mi? Ya da aslında çöpün yaşamı. Belki de bu olabilir. Çöpün nasıl oluştuğu vs. Fabrikada üretilmesi. İnsanlara dağıtılması. Ve sonra çöp olması. Çöp dağları oluşması. Çöp kutusunda yer alması. Neler yok ki çöp kutusunda. Bir sanatçı çöp kovasına attığı sanat işleri. Sanat işleri çöplükleri vs. Çöp kavramı aslında o kadar çok şey için geçerli ki? İşte bu çok çeşitli çöp kavramını ele almak gerekli. Yani objeler bir şekilde farklı konumlarda mekanlarda yer değiştiriyorlar. Bazen çöp oluyorlar bazen değerli vs.

% Bir bir çeşit çöp var. Bunlar binbir çeşit davranış sonucunda oluşuyorlar. Bir işlemin sonunda ortaya çıkan son ürün. Çöp konumuna gelmesi vs. Kime göre çöp neye göre çöp. Ama işte ortada bir konsensus yok. Başkaları da farklı şekilde görüyor. Birine göre çöp diğerine göre ise bir hazine.

% Dönüşmek ne oluyor peki bu durumda. Bir durumdan başka bir duruma geçmesi. Farklı bir anlam, amaç kazanması olabilir mi? Mesela pisuvar dönüşmüş müydü? Gazeteyi kolajda kullandığım zaman gazeteyi dönüştürmüş mü oluyorum? Hangisi dönüştü? Zaten buradaki açık bir şekilde açığa çıkıyor aslında. Her ikisi de dönüşmüş oluyor. Farklı bir kullanım alanı bulmak. Farklı niyetlerle kullanmak olabilir belki de. Bir şeyin ne zaman dönüştüğünü iddia edebilirsin.

% Agnes varda neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında sanatçıları da geziyor, çünkü onlar da topluyorlar. Onlar da o çöplerde farklı şeyler görüyorlar. Kendi de mesela çöpe atılmış bir şeye anlam yüklüyor. Kendisininde aslında bir toplayıcı olduğunun farkına varıyor.

%****************************************
% JUSTIFICATION (Gerekçesi)
% Eğer bir şeyin justificationından bahsediyorsak ben neleri iddia ediyorum:
% - Çöpü dönüştürdüğümü. Öncelikli olarak o gerçekten çöp mü? Sonrasında ise gerçekten dönüştü mü? (throw away culture çöpü anlatsa. rubbish theoryde dönüşümü anlatsa)
% - Peki neden bu işi yapıyorsun. Alternatifi aramak. Değer bulmak, değer bulunabilceğine inanmam aslında. Belki de değer üretmek için o değerleri yıkmak gerekli. Çöpe atıldığında bu yüzden bazı değerler yıkılıyordur. Artık yeni değerler vermek için gerekli yapı oluşuyordur o zaman. O yüzden çöpe atılması önemli. Bir yerin sonuna gelmiş olması aslında belki de yeni bir başlangıç olması için önemli olabilir. Çöplüğün bir başlangıç olması. Batırdığımız bitridiğimiz yerden yeni bir başlangıç. Çöpü üreten üretilmiş şeyleri bitiren zihniyetle tekar düşünmek. Aslında çöpe baktığında üretilen şeyin ne olduğunu tekrar sorguluyor olabilirsin. 
% - Çöp sanat işlerinde kullanılabilir. Bunlarla ilgili örnekler var.
% - Çöp bu sanat işlerinde dönüşmüştür. 
% - Elimdeki literatürden belli başlı argümanlar çıkarmalı, bu argümanlar benim yaptığım işi destekliyor demeli:
%........................................

>>>>

%****************************************
% Structure of this chapter
% Section: explain the topic and its significance, raise curiosity, give some facts about it.
% Section: state the the purpose of this study, specify the focus of it.
% Section: overview of chapters and structure of thesis.
% Section: a note on terminology, clarification about the comprehensive terminology.
%........................................

\epigraph{One can even shout out through refuse \ldots}{\hfill---Kurt Schwitters, \textit{Kurt Schwitters}, 1985}

%****************************************
% Rubbish: the archaeology of garbage. rathje1992rubbish
% Garbage project's findings have supplied a fresh perspective on what we know --- and what we think we know --- about certain aspects of our lives. p.24

% The basic methods of garbage disposal are four: dumping it, burning it, turning it into something that can be useful (recycling), and minimizing the volume of material goods.(p.33)

%ancient peoples p.33

%human behavior p.55 can you tell a lot about the customers from their garbage?

%p191-192 people tend to think of "recycling" as a relatively modern conceit that has only recently gained broad public acceptance, and whose practical benefits have only just began to be realized. Recycling itself is probably as old as --- indeed, seems to be a fundamental characteristic of --- human species.

%p.209 The reuse of paper, for example, involves processes that generated a considerable amount of hazardous waste. In order to recycle newspapers, magazines, and, indeed, any printed paper, the paper must first be de-inked. At the end of the de-inking process one is left with essentially two products: on the one hand, de-inked fiber that will be turned into new paper; and on th other, a large quantity of toxic sludge.
%........................................

%****************************************
% fast food packaging. p97

%trasformations during great depression, I learned firsthand about frugality as a child during ww2. my family carefully folded the wrapping paper from gifts to reuse on other occasions. p.8

% p11. for decades we've taken for granted used cars and old houses. Is there anyone alive who has always lived in new houses or driven only new cars?

% p.11 Economics has always been a factor in recycling.

% p.12 recycling is not limited to folk art.

% Bicycle wheel duchamp 1913.

% Use of recycled materials is not new, not is it exclusive to the united states. p.18

% p.22 Material, meaning, and memory --- these are artists' reasons for using found objects.

% p.48 recycling may be the most wasteful activity in modern America --- a waste of time and money, a waste of human and anutral resources. john tierney, "What a Waste," seattle postintelligencer...
%........................................

\comment{not shared thing, perception of waste is not static.} \paraphrase{"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others. The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions. Worthless. Rejected and useless matter of any kind. Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}}

@@

In previous ages (which age? pre industrial ages?) objects and resources are used again and again. Production of objects are hard and laborious. \comment{Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur. Mendillere bunlara örnek olabilir. Aslında tam benim konumla ilgili çünkü tek kullanımlık. Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.} \todo{Susan Strasser}

% Trash is everywhere and, produced every time
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession (It is experienced by everybody.). During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People do not care the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. They are durable(in terms of resistant to natural affects) products. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.)

Trash is global, and shared concept for all societies throughout the ages. 
\textbf{Trash in every age.} In other words it is part of human activity of every historic age. It exists early ages of human to now. Trash is part of the early days of human production / or activity. Firstly the word garbage is actually used for the parts of animal that cannot be consumed by the human. Legs, bones etc. [TODO etymology reference, see appendix] Archaeologist find things from people throw away. 
\textbf{Trash in every society.} Some of them called as trash the others don't. Somehow all actions of people generate trash. It is common. 
\textbf{Trash is everywhere.} in the streets, in your home, in the sea that you swam, around the globe(footnotes, satellite discard covers the atmosphere.).

% Introduction of ReVista
\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme. Yes and no. After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast. Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects. No one called it recycling. Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash. They can not handle their trash. There is no place for trash in their life.

@@

People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless? They do not think what happens after they throw it away. It exits from your life but not the world. What happens when you throw away a It is stacked from another place. Value of objects are not static. Trash is not static also It has a long journey. A project conducted by MIT researches journey of trash by placing trackers onto the trash. The results are surprising. Trashes spread away across the country and this journey takes month. \todo{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo{footnote what are these countries?}. In other worlds Americans trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo{consider Papua genen people}

@@

% ARTWORK
% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.

Why people are interested in rubbish. Some of the artist also interested in others trash. \comment{O çöplerde ne bulmayı umuyorlar ki? Aslında çöp bizim davranışlarımız, yaşayız tarzımız hakkında bize yön veriyor. ve bu her zaman fiziksel dönüştürme ile değil de aynı zamanda anlamsal ve mekansal değiştirme sorulamalarla mümkün oluyor. Bazen de olduğu gibi kullanıyorlar. bu açıdan önemli. Çöpü çöp şekliden sunan sanatçılar. Ama bu nasıl mümkün ki? fotoğrafını çekenler aslında gerçekten ona müdahele etmemiş mi oluyorlar. Bence değil? bir şekilde müdahele var gene orada. o fotoğraflarda artık dikkatin objesi haline geliyor. çöpün dönüşmesi aslında bir diğer yandan çöpe bakışın değişmesi olarak görülebilir.}

@@

% TODO Life time of objects.
% Nesnelerin yaşam süreleri, Bu yaşam sürelerinin ne kadar olduğu. Burada ilginç bilgiler olabilir. Aslında ne kadar çok üretip ne kadar kısa sürede tükettiğimi görüyoruz. Ama eskiden ürünler daha uzun sürelerde kullanılıyordı. Sonrasında ise bu kısa sürede tüketilen ürünlerden nasıl dağlar oluşuyor. Çöpçü kaç günde bir ziyaret ediyor. Çöp kutuları ne kadar sürede bir doluyor. Çöp kovalarının içlerinde neler var. Neler yok ki? Sanat işleri bile var. / çok hızlı tükettiğimizi aslında chris jordan gösteriyor bize. Can you imagine how much plastic cup is being consumed every hour?

\todo{Background information about the thesis. Inspirational points. facts of trash\ldots}

@@

This trash phenomena catches the attention of artist. It is very human activity. In this context which trash? What type of discard. Human discard. trashes of human activity. items that belongs to human. commodities etc.

%****************************************
% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

% Herkes çöpü dönüştürmüyor, bazıları ise çöpe dönüştürüyor. Ama ben bununla ilgilenmiyorum aslında.
%........................................

\todo{ArtBin, trashing things?}

%****************************************
% Different types of trash
\todo{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}

The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages. It can be thought that when the complexity of trashed increased required effort to repair, reuse and recycle is also increase. Therefore for the ones that have no complex tools it is becoming harder to reuse objects. In other words objects become more complex their re-usage becomes less likely.  Different production process generates different types of trash. According to production process, decomposition process\ldots The approach to the different type of trash will be different. In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it. There are some trashes that are more close to the people. More easy to convert them. more easy to regain to the society. 
%........................................

%****************************************
% Different disciplines, Perspectives related with trash from different disciplines
\todo{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines. In other words there are different studies related with trash. Different approaches to the trash and son on.}

% From Trashion: The Return of Disposed, Bahar Emgin.
\paraphrase{Such a conceptualization of waste as “the degree zero of value” has been contested for some time in different disciplines, ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture.}

This is very important because the problem of trash is being tried to be handled by different disciplines. In other words there different approaches to the trash. Different problems, different solutions. Which perspective that I have. In what ways my project differs from them. The purpose is to participate people in this work, by collecting them etc. And also offer to transform it. Rescue it and than later transform it. In short, the difference between the other disciplines must be clear. 
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it (handled by the municipals generally).
\item Technological perspectives. (seeing trash as a design problem. developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? development in what sense?)
\end{itemize}
%........................................

%%%
%%%
%%%
\section{Purpose of the Study}
\todo{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}

The aim of this study is to explore the theories and methods in transformation of trash in the context of art and artistic act.

@@

As many people are inside the business of transforming trash through craft and so on. People on the streets looking for aluminum cans, glass bottles, plastic. They collect and sell them to survive. There are companies that are collect waste materials to regain them again the industry. In thesis they are not in the scope. People that give attention to the trash and behave artistic act is in the scope of this thesis.

\comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%%
%%%
%%% 
\section{Overview of Chapters}
This study is structured many examples of artworks in different part of the thesis. As the related topic or argument is presented example artwork is given at this moment. Immediately how artist replies this issue is illustrated. Thereby artworks are examined in the theoretical and cultural context. Art works are used as a supportive elements for the stated arguments. \comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.} \comment{Sanat eserlerinin tümüyle bir çözümlemesi her yerde yapılamamıştır, konuyla ilgili kısımlarına değinilmiştir.}

@@

\comment{The final section, procedural description, covers the process of the project from beginning to end. The final chapter is reserved for conclusion. The overall project is summed up and the significance and the purpose of the project is re-emphasized.}
